Stabilization-Free Virtual Element Methods

### 2022-05-29 stabfreevem.tex
some revisions

% \begin{abstract}
% \end{abstract}

@@

\section{Preliminaries}

@@

For a $d$-dimensional polytope $K$, let $\mathcal{F}(K)$ and $\mathcal{E}(K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of $K$ respectively. For $F\in\mathcal{F}(K)$, denote by $\boldsymbol{n}_{K,F}$ be the unit outward normal vector to $\partial K$, which will be abbreviate as $\boldsymbol{n}_F$ or $\boldsymbol{n}$ if not causing any confusion.

@@

Let $\{\mathcal {T}_h\}$ denote a family of partitions
of $\Omega$ into nonoverlapping simple polytopes with $h:=\max\limits_{K\in \mathcal {T}_h}h_K$
and $h_K:=\mbox{diam}(K)$.
Denote by $\mathcal F_h$ and $\mathcal F_h^i$ the set of all $(d-1)$-dimensional faces and interior $(d-1)$-dimensional faces of the partition $\mathcal T_h$.
Set $\mathcal F_h^{\partial}=\mathcal F_h\backslash\mathcal F_h^i$.
For any $F\in\mathcal{F}_h$,
let $h_F$ be its diameter and fix a unit normal vector $\boldsymbol{n}_F$.
For a piecewise smooth function $v$, define 
$$
\|v\|_{1,h}^2:=\sum_{K\in\mathcal T_h}\|v\|_{1,K}^2,\quad |v|_{1,h}^2:=\sum_{K\in\mathcal T_h}|v|_{1,K}^2.
$$

For domain $K$, we use $\boldsymbol{H}(\div, K)$ and $\boldsymbol{H}_0(\div, K)$ to denote the standard divergence vector spaces. 
For $F\in\mathcal F_h$ and smooth vector function $\boldsymbol{v}$, define surface divergence
$$
\div_F\boldsymbol{v}=\div(\boldsymbol{v}-(\boldsymbol{v}\cdot\boldsymbol{n})\boldsymbol{n})=\div\boldsymbol{v}-\partial_n(\boldsymbol{v}\cdot\boldsymbol{n}).
$$

\subsection{Mesh conditions}
We impose the following conditions on the mesh $\mathcal T_h$ in this paper:
\begin{itemize}
 \item[(A1)] Each element $K\in \mathcal T_h$ and each face $F\in \mathcal F_h^r$ for $1\leq r\leq n-1$ is star-shaped with a uniformly bounded chunkiness parameter.

@@

For $K\in \mathcal T_h$, let $\boldsymbol{x}_K$ be the center of  the largest ball contained in $K$.
Throughout this paper, we use
``$\lesssim\cdots $" to mean that ``$\leq C\cdots$", where
$C$ is a generic positive constant independent of mesh size $h$, but may depend on the chunkiness parameter of the polytope, the degree of polynomials $k$, the dimension of space $n$, and the shape regularity and quasi-uniform constants of the virtual triangulation $\mathcal T^*_h$,
which may take different values at different appearances. And $A\eqsim B$ means $A\lesssim B$ and $B\lesssim A$.

For polytope $K\in \mathcal T_h$, denote by $\mathcal T_K$ the simplicial partition of $K$, which is induced from $\mathcal T_h^*$. Let $\mathcal{F}(\mathcal T_K)$ and $\mathcal{E}(\mathcal T_K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of the simplicial partition $\mathcal T_K$ respectively. Set 
$$
\mathcal{F}^{\partial}(\mathcal T_K):=\{F\in\mathcal{F}(\mathcal T_K): F\subset\partial K\},\quad \mathcal{E}^{\partial}(\mathcal T_K):=\{e\in\mathcal{E}(\mathcal T_K): e\subset\partial K\}.
$$
Denote $
\mathcal{F}^i(\mathcal T_K):=\mathcal{F}(\mathcal T_K)\backslash\mathcal{F}^{\partial}(\mathcal T_K)$ and $\mathcal{E}^i(\mathcal T_K):=\mathcal{E}(\mathcal T_K)\backslash\mathcal{E}^{\partial}(\mathcal T_K).
$

%Note that (A1) and (A2) imply ${\rm diam}(F) \eqsim {\rm diam} (K)$ for all $F\in \mathcal F^r(K), 1\leq r\leq n-1$.
%For a star-shaped domain $D$,

\section{$H(\div)$-Conforming Macro Finite Element}

In this section we will construct $H(\div)$-conforming macro finite element in arbitrary dimension.
\subsection{$H(\div)$-conforming finite element}
For each polygon $K\in \mathcal T_h$ and $k\geq2$, let 
$$
\boldsymbol{V}_{k-1}^{BDM}(K):=\{\boldsymbol{\phi}\in\bs H(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{k-1}(T;\mathbb R^d) \textrm{ for each } T\in\mathcal T_K\}
$$ 
be the local Brezzi-Douglas-Marini (BDM) element space~\cite{BrezziDouglasMarini1986,BrezziDouglasDuranFortin1987,Nedelec:1986family}, whose DoFs are given by (cf. \cite{ChenHuang2021divdiv})
\begin{align}
(\boldsymbol{v}\cdot\boldsymbol{n}, q)_F, & \quad q\in \mathbb P_{k-1}(F), F\in\mathcal F(T), \label{BDMdof1} \\
(\div\boldsymbol{v}, q)_T, & \quad q\in \mathbb P_{k-2}(T)/\mathbb R, \label{BDMdof2} \\
(\boldsymbol{v}, \boldsymbol{q})_T, & \quad \boldsymbol{q}\in \mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x}. \label{BDMdof3}
\end{align}
Define $\mathring{\boldsymbol{V}}_{k-1}^{BDM}(K):=\boldsymbol{V}_{k-1}^{BDM}(K)\cap \boldsymbol{H}_0(\div, K)$.

@@

By Lemma 3.12 in \cite{ChenHuang2021divdiv}, we have
\begin{equation}\label{eq:Pkvectordecomp}  
\mathbb P_{k-1}(T;\mathbb R^{d})=\nabla P_k(T)\oplus\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}.
\end{equation}

@@

\begin{lemma}
It holds the decomposition
\begin{equation}\label{eq:Pkskwtensordecomp}  
\mathbb P_{k-2}(T;\mathbb K)=\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\oplus\big(\mathbb P_{k-2}(T,\mathbb K)\cap\ker(\boldsymbol{x})\big).
\end{equation}
\end{lemma}
\begin{proof}
Thanks to decomposition \eqref{eq:Pkvectordecomp}, we have 
$$
\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\skw\nabla(\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}).
$$
By Lemma~\ref{lem:skwgrad}, $\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\cap\big(\mathbb P_{k-2}(T,\mathbb K)\cap\ker(\boldsymbol{x})\big)=\{\boldsymbol{0}\}$. Then we only need to check dimensions.
Due to complex \eqref{eq:polycomplex1},
\begin{equation}\label{eq:20220324-1}  
\dim\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\dim\mathbb P_{k-1}(T;\mathbb R^d)-\dim\nabla\mathbb P_k(T).
\end{equation}
On the other side, by space decomposition \eqref{eq:Pkvectordecomp},
$$
\dim\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}=\dim\mathbb P_{k-1}(T;\mathbb R^{d})-\dim\nabla\mathbb P_k(T).
$$
Hence $\dim\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\dim\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$, which yields \eqref{eq:Pkskwtensordecomp}.
\end{proof}

@@

Assume $\boldsymbol{\tau}\in\mathbb P_k(T;\mathbb K)$ and all the degrees of freedom \eqref{eq:-2formfemdof1}-\eqref{eq:-2formfemdof32} vanish. 
It holds from Lemma~\ref{lem:-2formfemfaceunisolvence} that $\boldsymbol{\tau}\boldsymbol{n}|_{\partial T}=\boldsymbol{0}$. Noting that $\boldsymbol{\tau}$ is antisymmetric,  we also have $\boldsymbol{n}^{\intercal}\boldsymbol{\tau}|_{\partial T}=\boldsymbol{0}$. On each $F\in\mathcal F(T)$, it holds
\begin{equation}\label{eq:20220324-3}
\boldsymbol{n}^{\intercal}\div\boldsymbol{\tau}=\div(\boldsymbol{n}^{\intercal}\boldsymbol{\tau})= \div_F(\boldsymbol{n}^{\intercal}\boldsymbol{\tau})+\partial_n(\boldsymbol{n}^{\intercal}\boldsymbol{\tau}\boldsymbol{n})=\div_F(\boldsymbol{n}^{\intercal}\boldsymbol{\tau}).
\end{equation}
Hence $\boldsymbol{n}^{\intercal}\div\boldsymbol{\tau}|_{\partial T}=0$. 
Thanks to DoFs \eqref{BDMdof1}-\eqref{BDMdof3} for BDM element, we acquire from DoF \eqref{eq:-2formfemdof31} that $\div\boldsymbol{\tau}=\boldsymbol{0}$, which together with DoF \eqref{eq:-2formfemdof32} and decomposition \eqref{eq:Pkskwtensordecomp} gives
$$
(\boldsymbol{\tau}, \boldsymbol{q})_T=0  \quad \forall~\boldsymbol{q}\in \mathbb P_{k-2}(T;\mathbb K).
$$
Applying Lemma~\ref{lem:PkKbubblecharac}, $\boldsymbol{\tau}$ has the expression as in \eqref{eq:PkKbubblecharac}. Taking $\boldsymbol{q}=q_{ij}\skw({\boldsymbol n_i\boldsymbol n_j^{\intercal}})$ in the last equation for $1\leq i<j\leq d$, we get $q_{ij}=0$. Thus $\boldsymbol{\tau}=\boldsymbol{0}$.
\end{proof}

For polygon $K\in \mathcal T_h$, define local finite element space for differential $(d-2)$-form  
\begin{align*}  
\boldsymbol{V}_{k}^{d-2}(K):=\{\boldsymbol{\tau}\in\bs L^2(K;\mathbb K)&: \boldsymbol{\tau}|_{T}\in \mathbb P_{k}(T;\mathbb K) \textrm{ for each } T\in\mathcal T_K, \\
&\;\;\textrm{ all the DoFs \eqref{eq:-2formfemdof1}-\eqref{eq:-2formfemdof22} are single-valued}\}.
\end{align*}
Thanks to Lemma~\ref{lem:-2formfemfaceunisolvence}, space $\boldsymbol{V}_{k}^{d-2}(K)$ is $H\Lambda^{d-2}$-conforming.
Define $\mathring{\boldsymbol{V}}_{k}^{d-2}(K):=\boldsymbol{V}_{k}^{d-2}(K)\cap \mathring{H}\Lambda^{d-2}(K)$, where $\mathring{H}\Lambda^{d-2}(K)$ is the subspace of $H\Lambda^{d-2}(K)$ with homogeneous boundary condition.
Notice that
 $\boldsymbol{V}_{k}^{d-2}(K)$ is the Lagrange element space for $d=2$,
and $\boldsymbol{V}_{k}^{d-2}(K)$ is the second kind N\'ed\'elec element space for $d=3$ \cite{Nedelec:1986family}.

@@

Next prove $\boldsymbol{V}_{k-1}^{BDM}(K)\cap\ker(\div)=\div\skw\boldsymbol{V}_{k}^{d-2}(K)$. For $\boldsymbol{v}\in\boldsymbol{V}_{k-1}^{BDM}(K)\cap\ker(\div)$, by Theorem 1.1 in \cite{CostabelMcIntosh2010}, there exists $\boldsymbol{\tau}\in\boldsymbol{H}^1(K;\mathbb K)$ satisfying $\div\boldsymbol{\tau}=\div\skw\boldsymbol{\tau}=\boldsymbol{v}$. Let $\boldsymbol{\sigma}\in \boldsymbol{V}_{k}^{d-2}(K)$ be the nodal interpolation of $\boldsymbol{\tau}$ based on DoFs \eqref{eq:-2formfemdof1}-\eqref{eq:-2formfemdof32}. Thanks to DoF \eqref{eq:-2formfemdof1}, it follows from the integration by parts that
$$
(\div_F(\boldsymbol{\sigma}\boldsymbol{n}), 1)_F=(\boldsymbol{v}, 1)_F\quad\forall~F\in\mathcal F(\mathcal T_K),
$$
which together with \eqref{eq:20220324-3} and DoF \eqref{eq:-2formfemdof21} that
$$
(\boldsymbol{n}^{\intercal}\div\boldsymbol{\sigma}, q)_F = (\div_F(\boldsymbol{\sigma}\boldsymbol{n}), q)_F=(\boldsymbol{v}\cdot\boldsymbol{n}, q)_F\quad\forall~q\in \mathbb P_{k-1}(F),F\in\mathcal F(\mathcal T_K).
$$
Therefore, due to DoF \eqref{eq:-2formfemdof31} and the fact $\div\div\boldsymbol{\sigma}=\div\boldsymbol{v}=0$,
we acquire from the unisolvence of DoFs \eqref{BDMdof1}-\eqref{BDMdof3} for BDM element that $\boldsymbol{v}=\div\boldsymbol{\sigma} \in \div\skw\boldsymbol{V}_{k}^{d-2}(K)$.
\end{proof}

@@

Let 
$$
\mathbb{V}_{k-1}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K): \boldsymbol{\phi}\cdot\boldsymbol{n}|_F\in\mathbb P_{k-1}(F) \quad\forall~F\in\mathcal F(K)\}.
$$
Due to DoFs \eqref{Vpdivdof1}-\eqref{Vpdivdof3} for $\boldsymbol{V}_{k-1}^{\rm div}(K)$, a set of unisolvent DoFs for $\mathbb{V}_{k-1}^{\rm div}(K)$ is 
\begin{align}
    (\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F & \quad\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in\mathcal F(K), \label{Vpdivdof1}\\
    (\div\boldsymbol{\phi}, q)_K & \quad\forall~q\in\mathbb P_{\max\{k-2,0\}}(K)/\mathbb R, \label{Vpdivdof2} \\
    (\boldsymbol{\phi}, \bs q)_K & \quad\forall~\bs q\in \div\mathring{\boldsymbol{V}}_{k}^{d-2}(K). \label{Vpdivdof3}
\end{align}
For later use, let $Q_{K,k-1}^{\div}$ be the $L^2$-orthogonal projection operator onto $\mathbb{V}_{k-1}^{\rm div}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
Introduce discrete spaces
\begin{align*}
\mathbb{V}_{h,k-1}^{\rm div}&:=\{\boldsymbol{\phi}_h\in \boldsymbol{L}^2(\Omega;\mathbb R^d): \boldsymbol{\phi}_h|_K\in \mathbb{V}_{k-1}^{\rm div}(K) \textrm{ for each } K\in\mathcal T_h\}, \\
\mathbb P_l(\mathcal T_h)&:=\{q_h\in L^2(\Omega): q_h|_K\in \mathbb P_l(K) \textrm{ for each } K\in\mathcal T_h\}
\end{align*}
with non-negative integer $l$.
For $\boldsymbol{\phi}\in\boldsymbol{L}^2(\Omega;\mathbb R^d)$, let $Q_{h,k-1}^{\div}\boldsymbol{\phi}\in\mathbb{V}_{h,k-1}^{\rm div}$ be determined by $(Q_{h,k-1}^{\div}\boldsymbol{\phi})|_K=Q_{K,k-1}^{\div}(\boldsymbol{\phi}|_K)$ for each $K\in\mathcal T_h$. For $v\in L^2(\Omega)$, let $Q_h^lv\in \mathbb P_l(\mathcal T_h)$ be determined by $(Q_h^{l}v)|_K=Q_{l}^K(v|_K)$ for each $K\in\mathcal T_h$. For simplicity, the vector version of $Q_h^l$ is still denoted by $Q_h^l$. And we abbreviate $Q_h^k$ as $Q_h$ if $l=k$.

@@

\section{Stabilization-free nonconforming virtual element method}

@@

@@

>>>>

\begin{abstract}
Stabilization-free virtual element methods in arbitrary degree of polynomial are developed for second order elliptic problems, including a nonconforming virtual element method in arbitrary dimension and a conforming virtual element method in two dimensions.

\end{abstract}

@@

\section{Introduction}

Recently a stabilization-free linear virtual element method, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022}, where the degree of polynomial used in projection depends on the number of vertices of the polygon. We refer to~\cite{DAltriMirandaPatrunoSacco2021} for a discussion on smiliar stabilization-free virtual element methods for plane elasticity problem.
The idea in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022} is not easy to extend to construct higher order stabilization-free virtual element methods, and
the analysis is rather elaborate. 
This motives us to construct stabilization-free virtual element methods in arbitrary degree of polynomial and arbitrary dimension in a unified way.

The rest of this paper is organized as follows. Notation and mesh conditions are presented in Section~\ref{sec:prelim}. 
In Section~\ref{sec:divmacrofem}, $H(\div)$-conforming macro finite elements in arbitrary dimension are constructed. A stabilization-free nonconforming virtual element method in arbitrary dimension is developed in Section \ref{sec:stabfreencfmvem}. And a stabilization-free conforming virtual element method in two dimensions is devised in Section \ref{sec:stabfreecfmvem}.
Some numerical results are shown in Section \ref{sec:numericalexamps}.

\section{Preliminaries}\label{sec:prelim}

@@

For $d$-dimensional polytope $K$, let $\mathcal{F}(K)$ and $\mathcal{E}(K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of $K$ respectively. For $F\in\mathcal{F}(K)$, denote by $\boldsymbol{n}_{K,F}$ be the unit outward normal vector to $\partial K$, which will be abbreviate as $\boldsymbol{n}_F$ or $\boldsymbol{n}$ if not causing any confusion.

@@

Let $\{\mathcal {T}_h\}$ denote a family of partitions
of $\Omega$ into nonoverlapping simple polytopes with $h:=\max\limits_{K\in \mathcal {T}_h}h_K$
and $h_K:=\mbox{diam}(K)$.
Denote by $\mathcal F_h^r$ the set of all $(d-r)$-dimensional faces of the partition $\mathcal T_h$ for $r=1,\ldots,d$. Set $\mathcal F_h:=\mathcal F_h^1$ for simplicity. Let $\mathcal F_h^{\partial}$ be the subset of $\mathcal F_h$ including all $(d-1)$-dimensional faces on $\partial\Omega$. 
For any $F\in\mathcal{F}_h$,
let $h_F$ be its diameter and fix a unit normal vector $\boldsymbol{n}_F$.
For a piecewise smooth function $v$, define 
$$
\|v\|_{1,h}^2:=\sum_{K\in\mathcal T_h}\|v\|_{1,K}^2,\quad |v|_{1,h}^2:=\sum_{K\in\mathcal T_h}|v|_{1,K}^2.
$$

For domain $K$, we use $\boldsymbol{H}(\div, K)$ and $\boldsymbol{H}_0(\div, K)$ to denote the standard divergence vector spaces. 
For smooth vector function $\boldsymbol{v}$, let $\nabla\boldsymbol{v}:=(\partial_iv_j)_{1\leq i,j\leq d}$.
On face $F\in\mathcal F_h$, define surface divergence
$$
\div_F\boldsymbol{v}=\div(\boldsymbol{v}-(\boldsymbol{v}\cdot\boldsymbol{n})\boldsymbol{n})=\div\boldsymbol{v}-\partial_n(\boldsymbol{v}\cdot\boldsymbol{n}).
$$
For smooth function $v$, define surface gradient $\nabla_Fv:=\nabla v-(\partial_nv)\boldsymbol{n}$.

\subsection{Mesh conditions}
We impose the following conditions on the mesh $\mathcal T_h$ in this paper:
\begin{itemize}
 \item[(A1)] Each element $K\in \mathcal T_h$ and each face $F\in \mathcal F_h^r$ for $1\leq r\leq d-1$ is star-shaped with a uniformly bounded chunkiness parameter.

@@

For $K\in \mathcal T_h$, let $\boldsymbol{x}_K$ be the center of  the largest ball contained in $K$.
Throughout this paper, we use
``$\lesssim\cdots $" to mean that ``$\leq C\cdots$", where
$C$ is a generic positive constant independent of mesh size $h$, but may depend on the chunkiness parameter of the polytope, the degree of polynomials $k$, the dimension of space $d$, and the shape regularity and quasi-uniform constants of the virtual triangulation $\mathcal T^*_h$,
which may take different values at different appearances. And $A\eqsim B$ means $A\lesssim B$ and $B\lesssim A$.

For polytope $K\in \mathcal T_h$, denote by $\mathcal T_K$ the simplicial partition of $K$, which is induced from $\mathcal T_h^*$. Let $\mathcal{F}(\mathcal T_K)$ and $\mathcal{E}(\mathcal T_K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of the simplicial partition $\mathcal T_K$ respectively. Set 
$$
\mathcal{F}^{\partial}(\mathcal T_K):=\{F\in\mathcal{F}(\mathcal T_K): F\subset\partial K\},\quad \mathcal{E}^{\partial}(\mathcal T_K):=\{e\in\mathcal{E}(\mathcal T_K): e\subset\partial K\}.
$$

Hereafter we use $T$ to represent a simplex, and $K$ to denote a general polytope.

\section{$H(\div)$-Conforming Macro Finite Elements}\label{sec:divmacrofem}

In this section we will construct $H(\div)$-conforming macro finite elements in arbitrary dimension.
\subsection{$H(\div)$-conforming finite elements}
For polygon $K\in \mathcal T_h$ and $k\geq2$, let 
$$
\boldsymbol{V}_{k-1}^{BDM}(K):=\{\boldsymbol{\phi}\in\bs H(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{k-1}(T;\mathbb R^d) \textrm{ for each } T\in\mathcal T_K\}
$$ 
be the local Brezzi-Douglas-Marini (BDM) element space~\cite{BrezziDouglasMarini1986,BrezziDouglasDuranFortin1987,Nedelec:1986family}, whose degrees of freedom (DoFs) are given by \cite{ChenHuang2021divdiv}
\begin{align}
(\boldsymbol{v}\cdot\boldsymbol{n}, q)_F, & \quad q\in \mathbb P_{k-1}(F), F\in\mathcal F(T), \label{BDMdof1} \\
(\div\boldsymbol{v}, q)_T, & \quad q\in \mathbb P_{k-2}(T)/\mathbb R, \label{BDMdof2} \\
(\boldsymbol{v}, \boldsymbol{q})_T, & \quad \boldsymbol{q}\in \mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x}. \label{BDMdof3}
\end{align}
Define $\mathring{\boldsymbol{V}}_{k-1}^{BDM}(K):=\boldsymbol{V}_{k-1}^{BDM}(K)\cap \boldsymbol{H}_0(\div, K)$.

@@

By Lemma 3.12 in \cite{ChenHuang2021divdiv}, we have the decomposition
\begin{equation}\label{eq:Pkvectordecomp}  
\mathbb P_{k-1}(T;\mathbb R^{d})=\nabla P_k(T)\oplus\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}.
\end{equation}

@@

\begin{lemma}
It holds the decomposition
\begin{equation}\label{eq:Pkskwtensordecomp}  
\mathbb P_{k-2}(T;\mathbb K)=\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\oplus\big(\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x})\big).
\end{equation}
\end{lemma}
\begin{proof}
Thanks to decomposition \eqref{eq:Pkvectordecomp}, we have 
$$
\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\skw\nabla(\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}).
$$
By Lemma~\ref{lem:skwgrad}, $\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\cap\big(\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x})\big)=\{\boldsymbol{0}\}$. Then we only need to check dimensions.
Due to complex \eqref{eq:polycomplex1},
\begin{equation}\label{eq:20220324-1}  
\dim\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\dim\mathbb P_{k-1}(T;\mathbb R^d)-\dim\nabla\mathbb P_k(T).
\end{equation}
On the other side, by space decomposition \eqref{eq:Pkvectordecomp},
$$
\dim\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}=\dim\mathbb P_{k-1}(T;\mathbb R^{d})-\dim\nabla\mathbb P_k(T).
$$
Hence $\dim\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\dim\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$, which yields \eqref{eq:Pkskwtensordecomp}.
\end{proof}

@@

Assume $\boldsymbol{\tau}\in\mathbb P_k(T;\mathbb K)$ and all the degrees of freedom \eqref{eq:-2formfemdof1}-\eqref{eq:-2formfemdof32} vanish. 
It holds from Lemma~\ref{lem:-2formfemfaceunisolvence} that $\boldsymbol{\tau}\boldsymbol{n}|_{\partial T}=\boldsymbol{0}$. Noting that $\boldsymbol{\tau}$ is antisymmetric,  we also have $\boldsymbol{n}^{\intercal}\boldsymbol{\tau}|_{\partial T}=\boldsymbol{0}$. On each $F\in\mathcal F(T)$, it holds
\begin{equation}\label{eq:20220324-3}
\boldsymbol{n}^{\intercal}\div\boldsymbol{\tau}=\div(\boldsymbol{n}^{\intercal}\boldsymbol{\tau})= \div_F(\boldsymbol{n}^{\intercal}\boldsymbol{\tau})+\partial_n(\boldsymbol{n}^{\intercal}\boldsymbol{\tau}\boldsymbol{n})=\div_F(\boldsymbol{n}^{\intercal}\boldsymbol{\tau}).
\end{equation}
Hence $\boldsymbol{n}^{\intercal}\div\boldsymbol{\tau}|_{\partial T}=0$. 
Thanks to DoFs \eqref{BDMdof1}-\eqref{BDMdof3} for BDM element, we acquire from DoF \eqref{eq:-2formfemdof31} and $\div\div\boldsymbol{\tau}=0$ that $\div\boldsymbol{\tau}=\boldsymbol{0}$, which together with DoF \eqref{eq:-2formfemdof32} and decomposition \eqref{eq:Pkskwtensordecomp} gives
$$
(\boldsymbol{\tau}, \boldsymbol{q})_T=0  \quad \forall~\boldsymbol{q}\in \mathbb P_{k-2}(T;\mathbb K).
$$
Applying Lemma~\ref{lem:PkKbubblecharac}, $\boldsymbol{\tau}$ has the expression as in \eqref{eq:PkKbubblecharac}. Taking $\boldsymbol{q}=q_{ij}\skw({\boldsymbol n_i\boldsymbol n_j^{\intercal}})$ in the last equation for $1\leq i<j\leq d$, we get $q_{ij}=0$. Thus $\boldsymbol{\tau}=\boldsymbol{0}$.
\end{proof}

For polygon $K\in \mathcal T_h$, define the local finite element space for differential $(d-2)$-form  
\begin{align*}  
\boldsymbol{V}_{k}^{d-2}(K):=\{\boldsymbol{\tau}\in\bs L^2(K;\mathbb K)&: \boldsymbol{\tau}|_{T}\in \mathbb P_{k}(T;\mathbb K) \textrm{ for each } T\in\mathcal T_K, \\
&\;\;\textrm{ all the DoFs \eqref{eq:-2formfemdof1}-\eqref{eq:-2formfemdof22} are single-valued}\}.
\end{align*}
Thanks to Lemma~\ref{lem:-2formfemfaceunisolvence}, space $\boldsymbol{V}_{k}^{d-2}(K)$ is $H\Lambda^{d-2}$-conforming.
Define $\mathring{\boldsymbol{V}}_{k}^{d-2}(K):=\boldsymbol{V}_{k}^{d-2}(K)\cap \mathring{H}\Lambda^{d-2}(K)$, where $\mathring{H}\Lambda^{d-2}(K)$ is the subspace of $H\Lambda^{d-2}(K)$ with homogeneous boundary condition.
Notice that
 $\boldsymbol{V}_{k}^{d-2}(K)$ is the Lagrange element space for $d=2$,
and $\boldsymbol{V}_{k}^{d-2}(K)$ is the second kind N\'ed\'elec element space for $d=3$ \cite{Nedelec:1986family}.

@@

Next prove $\boldsymbol{V}_{k-1}^{BDM}(K)\cap\ker(\div)=\div\skw\boldsymbol{V}_{k}^{d-2}(K)$. For $\boldsymbol{v}\in\boldsymbol{V}_{k-1}^{BDM}(K)\cap\ker(\div)$, by Theorem 1.1 in \cite{CostabelMcIntosh2010}, there exists $\boldsymbol{\tau}\in\boldsymbol{H}^1(K;\mathbb K)$ satisfying $\div\boldsymbol{\tau}=\div\skw\boldsymbol{\tau}=\boldsymbol{v}$. Let $\boldsymbol{\sigma}\in \boldsymbol{V}_{k}^{d-2}(K)$ be the nodal interpolation of $\boldsymbol{\tau}$ based on DoFs \eqref{eq:-2formfemdof1}-\eqref{eq:-2formfemdof32}. Thanks to DoF \eqref{eq:-2formfemdof1}, it follows from the integration by parts that
$$
(\div_F(\boldsymbol{\sigma}\boldsymbol{n}), 1)_F=(\boldsymbol{v}\cdot\boldsymbol{n}, 1)_F\quad\forall~F\in\mathcal F(\mathcal T_K),
$$
which together with \eqref{eq:20220324-3} and DoF \eqref{eq:-2formfemdof21} that
$$
(\boldsymbol{n}^{\intercal}\div\boldsymbol{\sigma}, q)_F = (\div_F(\boldsymbol{\sigma}\boldsymbol{n}), q)_F=(\boldsymbol{v}\cdot\boldsymbol{n}, q)_F\quad\forall~q\in \mathbb P_{k-1}(F),F\in\mathcal F(\mathcal T_K).
$$
Therefore, due to DoF \eqref{eq:-2formfemdof31} and the fact $\div\div\boldsymbol{\sigma}=\div\boldsymbol{v}=0$,
we acquire from the unisolvence of DoFs \eqref{BDMdof1}-\eqref{BDMdof3} for BDM element that $\boldsymbol{v}=\div\boldsymbol{\sigma} \in \div\skw\boldsymbol{V}_{k}^{d-2}(K)$.
\end{proof}

@@

Let 
$$
\mathbb{V}_{k-1}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K): \boldsymbol{\phi}\cdot\boldsymbol{n}|_F\in\mathbb P_{k-1}(F) \quad\forall~F\in\mathcal F(K)\}.
$$
Due to DoFs \eqref{Vpdivdof1}-\eqref{Vpdivdof3} for $\boldsymbol{V}_{k-1}^{\rm div}(K)$, a set of unisolvent DoFs for $\mathbb{V}_{k-1}^{\rm div}(K)$ is 
\begin{align}
    (\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F & \quad\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in\mathcal F(K), \label{Vpdivdof1}\\
    (\div\boldsymbol{\phi}, q)_K & \quad\forall~q\in\mathbb P_{\max\{k-2,0\}}(K)/\mathbb R, \label{Vpdivdof2} \\
    (\boldsymbol{\phi}, \bs q)_K & \quad\forall~\bs q\in \div\mathring{\boldsymbol{V}}_{k}^{d-2}(K). \label{Vpdivdof3}
\end{align}

@@

For later use, let $Q_{K,k-1}^{\div}$ be the $L^2$-orthogonal projection operator onto $\mathbb{V}_{k-1}^{\rm div}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
Introduce discrete spaces
\begin{align*}
\mathbb{V}_{h,k-1}^{\rm div}&:=\{\boldsymbol{\phi}_h\in \boldsymbol{L}^2(\Omega;\mathbb R^d): \boldsymbol{\phi}_h|_K\in \mathbb{V}_{k-1}^{\rm div}(K) \textrm{ for each } K\in\mathcal T_h\}, \\
\mathbb P_l(\mathcal T_h)&:=\{q_h\in L^2(\Omega): q_h|_K\in \mathbb P_l(K) \textrm{ for each } K\in\mathcal T_h\}
\end{align*}
with non-negative integer $l$.
For $\boldsymbol{\phi}\in\boldsymbol{L}^2(\Omega;\mathbb R^d)$, let $Q_{h,k-1}^{\div}\boldsymbol{\phi}\in\mathbb{V}_{h,k-1}^{\rm div}$ be determined by $(Q_{h,k-1}^{\div}\boldsymbol{\phi})|_K=Q_{K,k-1}^{\div}(\boldsymbol{\phi}|_K)$ for each $K\in\mathcal T_h$. For $v\in L^2(\Omega)$, let $Q_h^lv\in \mathbb P_l(\mathcal T_h)$ be determined by $(Q_h^{l}v)|_K=Q_{l}^K(v|_K)$ for each $K\in\mathcal T_h$. For simplicity, the vector version of $Q_h^l$ is still denoted by $Q_h^l$. And we abbreviate $Q_h^k$ as $Q_h$ if $l=k$.

\section{Stabilization-free nonconforming virtual element method}\label{sec:stabfreencfmvem}

@@

For polygon $K\subset\mathbb R^2$, let $\mathcal{V}(K)$ be the set of all vertices of $K$. And we overload notation $\mathcal{E}(K)$ to denote the set of all edges of $K$ in this section.

@@

It is obvious that 
\begin{equation}\label{eq:cfmahbounedness}
a_h(u, v)\lesssim |u|_1|v|_1\quad\forall~u,v\in H_0^1(\Omega).
\end{equation}  
And the norm equivalence \eqref{eq:cfmgradVknormequivalence} implies
the coercivity
\begin{equation}\label{eq:cfmahcoercivity}
|v_h|_1^2\lesssim a_h(v_h, v_h)\quad\forall~v_h\in V_h.
\end{equation}  
Therefore the stabilization-free virtual element method \eqref{eq:cfmvem} is uni-solvent.
